\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip} 	
\usepackage{color}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{array}
\usepackage{supertabular}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=\textbullet]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

\begin{document}
\pagestyle{empty} 

%---------------------- TITLE --------------------------
\begin{tabularx}{\linewidth}{>{\centering\arraybackslash}X}
\Huge{Siddhant Gaikwad} \\[5pt]
\small Pune, Maharashtra, India \\[7.5pt]
\href{mailto:siddhant.gaikwad1754@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ siddhant.gaikwad1754@gmail.com} \ $|$ \ 
\href{tel:+919322857003}{\raisebox{-0.05\height}\faMobile\ +91-9322857003} \ $|$ \
\href{https://www.linkedin.com/in/siddhant-gaikwad-50335b270/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{https://github.com/S0ulReaPeR1}{\raisebox{-0.05\height}\faGithub\ Github}
\end{tabularx}


%---------------------- SUMMARY --------------------------
\section{Summary}
Computer Science student with expertise in full-stack web development, system design, and scalable application development. Proficient in building high-performance web applications, integrating databases, and APIs. Experienced in developing responsive UIs, secure backends, and real-time features. Passionate about problem solving, performance optimization, and user-centric development.

%---------------------- EDUCATION --------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
Nov 2022 – Present & \textbf{Vishwakarma Institute of Technology, Pune} \hfill Pune, India \\
& Bachelor of Technology — Computer Science \hfill (CGPA: 8.75) \\
\end{tabularx}
%---------------------- SKILLS --------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages & JavaScript, Java, Python, C \\
Web Technologies & React, Node.js, Express.js, Flask, Spring Boot, MySQL, MongoDB, TailwindCSS \\
Tools & Figma, Git/GitHub, VS Code, Spring Tool Suite \\
Soft Skills & Leadership, Communication, Teamwork, Public Speaking
\end{tabularx}
%---------------------- EXPERIENCE --------------------------
\section{Experience}
\begin{joblong}{Industry Project Intern — E-Zest by Accion Labs}{Mar 2025 – Sep 2025}
\item Developed a full-stack calendar management application using React, Node.js, Express, and MongoDB with OAuth 2.0 authentication for Google and Microsoft integration.
\item Implemented an AI-powered conversational scheduling system with NLP that detects conflicts and suggests optimal meeting times via chatbot.
\item Delivered a production-ready web application with RESTful APIs, JWT authentication, and real-time chatbot integration.
\end{joblong}

%---------------------- PROJECTS --------------------------
\section{Projects}

\begin{joblong}{CraftConnect — Service Marketplace Platform}{Feb 2025 – Present}
\item Tech Stack: React, TailwindCSS, Node.js, MongoDB, Redis
\item Built a platform connecting professionals with customers for service bookings.
\item Implemented real-time location-based professional search and OTP verification with role-based authentication.
\end{joblong}

\begin{joblong}{Raga Music Generator — AI Research Project}{Nov 2024}
\item Tech Stack: Python, TensorFlow, LSTM, Deep Learning, Streamlit
\item Trained 4 AI models using a double LSTM architecture, improving raga accuracy by 35\%.
\item Processed 500+ music samples, achieving an 85\% accuracy rate by optimizing loss functions.
\end{joblong}

\begin{joblong}{AI-Based Email Phishing Detection using NLP}{Jan 2025 – May 2025}
\item Tech Stack: Python, PyTorch, Transformers, LSTM, Deep Learning
\item Built a BERT+LSTM hybrid model to detect phishing emails with high accuracy.
\item Implemented dataset handling classes, model saving/loading, and trained on diverse datasets.
\end{joblong}



\vfill
\center{\footnotesize Last updated: \today}

\end{document}
